---
title: "LinAlgPractice"
author: "Cassandra Manrique"
date: "6/21/2021"
output: html_document
---
On a sunny day, two tables are standing in an English country garden. On each
table birds of unknown species are sitting having the time of their lives.
A bird from the first table says to those on the second table: “Hi – if one of you
come to our table then there will be the same number of us on each table”. “Yeah,
right”, says a bird from the second table, “but if one of you comes to our table, then
we will be twice as many on our table as on yours”.
Question: How many birds are on each table? 

Let x=table 1 and y=table 2

System of equations:
x+1=y-1, or x-y=-2
2x=y+1, or 2x-y=1

```{r}
#matrices  
A<-matrix(c(1,2,-1,-1), 
          ncol=2)
B<-c(-2,1)

#solve
X<-solve(A)%*%B

#Solution matrix 
X
```

There are 3 birds on the first table and five birds on the second table. 

Plotting system of linear equations: Two unknowns
```{r}
A<-matrix(c(1,-1,2,2),
          nrow=2,
          ncol=2,
          byrow=TRUE)
B<-matrix(c(2,1),
          nrow=2,
          ncol=1,
          byrow=TRUE)

#Show the matrices
library(matlib)
matlib::showEqn(A,B)

#Plot the equations
plotEqn(A,B)

#Solve equations 
solve(A,B)
```

Three unknowns
```{r}
C<-matrix(c(2,1,-1,3,1,-2,2,-1,-2),
          nrow=3,
          ncol=3,
          byrow=TRUE)
d<-c(8,11,3)
matlib::showEqn(C,d)

solve(C,d)

matlib::plotEqn3d(C,d,
                  xlim=c(-4,4),
                  ylim=c(-4,4),
                  col=c("green","blue"),
                  alpha=1)
```

Vector Addition on Plots
```{r}
a<-c(1,1)
b<-c(3,-4)
x<-0
y<-0

plot(x,y,
     xlim=c(-1,4),
     ylim=c(-4,4))

#Vector A
arrows(0,0,a[1],a[2],col="red")
#Vector B
arrows(0,0,b[1],b[2],col="blue")
#Vector B on tip of A
arrows(a[1],a[2],(a[1]+b[1]),(a[2]+b[2]),
       col="blue",
       lty="dashed")
#Vector A+B
arrows(0,0,(a[1]+b[1]),(a[2]+b[2]),
       col="green")
#Legend
legend(-1,4,
       legend=c("Vector A","Vector B","Vector A+B"),
       lty=1,
       col=c("red","blue","green"))
```

Vector Addition in 3D
```{r}
options(rgl.printRglwidget = TRUE)

xyz<-matrix(c(1,2,
              5,-1,
              -4,2), nrow=3,ncol=2)
origin<-c(0,0,0)
spriteorigin=origin
plot3d(xyz,
       xlab="X",
       ylab="Y",
       zlab="Z")
arrow3d(origin,xyz[,1],
        type="lines",
        lwd=2,
        col="red")
arrow3d(origin,xyz[,2],
        type="lines",
        lwd=2,
        col="blue")
arrow3d(xyz[,1],(xyz[,1]+xyz[,2]),
        type="lines",
        lwd=0.5,
        col="blue")
arrow3d(origin,(xyz[,1]+xyz[,2]),
        type="lines",
        lwd=2,
        col="green")
```